Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012

### 2018-07-04 response-to-reviewers.tex

  \begin{response}
    No response needed here.
  \end{response}
\item 
  \debug{OT: should refer to Toomet (2011), maybe there are more
    papers.  The effect is mainly coming from Tallinn and somewhat
    from education too, either do a table that disentangles these, or
    a plot (violin plot?) by group.}
  \debug{SKB: I did the estimation separated by regions, but not 
  separated by regions and educational level. We could add the regional
  breakdown in the appendix or add it as another extension to chapter 6.}
  My main concern is with some of their wage results. I find it
  puzzling that they don’t find a wage premium for Russian men who
  have Estonian language skills as they do find a sizeable significant
  effect of about 11 to 17 percent for Russian women and a significant
  positive effect for Estonians who speak Russian. Furthermore, they
  find that Estonian language skills do reduce the probability of
  being unemployed for Russians. Why is there a reduction in the
  probability of being unemployed, but no wage effect? Can we trust
  this result? Looking at the descriptive statistics (see Table 1) the
  wage for Russian men who speak Estonian seems to be higher compared
  to Russian men without the ability to speak Estonian (489.96 vs
  401.59). The authors should either provide more statistics on this
  result (if possible) or a more detailed discussion on potential
  reasons that lead to this finding.
\item
  \debug{OT: I'll do a rewrite after changes are made, hope it's
    sufficient.} 
  The paper needs to be checked for spelling and grammar
  errors. There are a number of typos and errors, which should be
  corrected in a revision. This would normally be a minor comment, but
  here the authors should take this comment very serious as there are
  so many mistakes.
\end{enumerate}

\subsection{Minor comments:}

\begin{enumerate}
\item- The description of the estimation models in Chapter 4 should
  be more detailed. Please describe more specifically what exactly you
  are estimating. In particular the description of the second model
  estimating the time trend is very short.
  \debug{SKB: Svetlana modified the equations a bit. I added another table,
  which summarises the models.}
\item - The tables and figures should have notes that explain in more
  detail what is shown in the respective table and figure. For
  instance, the table notes should contain the included control
  variables, the sample period and the age restriction applied.
  \debug{SKB: I added this information to the tables and the figures. The descriptions might need some polishing still.}
\item 
- Page 4: You write that you are only analysing individuals who are
working or actively looking for a job, but in line 35 on the same page
you write that inactivity is one of the included labour market
outcomes. Please clarify this and be clear in your description of what
is included in your sample.
\item 
  \debug{ot: let's make it equal (i.e. remove all observations with
    any of the variables missing.  Add a footnote that when we
    included all the variables, we still got the same results.}
\debug{SKB: I estimated the models and updated tht.}
  The sample size for different specification of the same analysis
should be the equal. Otherwise it is difficult to conclude whether the
changes in the coefficients are coming from the addition of more
controls or form the change in the size of the estimation sample.
\item 
- In the paper, you are only showing the results of the variables of
interest. I suggest to provide tables including all coefficients (not
the year dummies) in the Appendix. It might be interesting to see how
the coefficients of the control variables change across the different
models.
\debug{SKB: Will add them after I figured out how to present the results nicely formatted. It boils down to finding the right options for the \enquote{estout} or the \enquote{outtex/outreg} user provided package in Stata. I could do the formatting in Excel myself, but I prefer the Stata solution. }
\item 
- All tables: Be consistent in the description of your tables. The
table notes and the labels for e.g., "observations", are inconsistent
across the different tables. 
\debug{SKB: Fixed. Changed obs to observations}
\item
  \debug{ot: this was because of both 'B. Chiswick' and
    'B. R. Chiswick' in the bibtex file, and bibtex wanted to
    distinguish between these two guys.}
 Page 1: To cite Chiswick you are using different versions
(B. Chiswick and B. R. Chiswick).

@@

\subsubsection*{6. Quality of Communication}

\begin{enumerate}
\item There appear to be a few grammatical/typo errors in
  the paper. This is not an exhaustive list, but: 
  \begin{enumerate}
  \item pg 1 ln 51 “an” is
    not needed. 
  \item Pg 2 ln43: maybe indent this paragraph. 
  \item ln 49 “We find
    that in the case of, Estonian language is associated…” maybe missing
    the word “the”  
  \item ln 54 and 57: its instead of “it’s” 
  \item ln 58 and 59
    “that [the] Estonian…” and “boundaries, men [are] more…” 
  \item Pg. 16 ln
    45-50 The whole paragraph feels a little awkward. 
  \item I also do not know
    what “cv.ee” means.
    \debug{SKB: We should set a link or further explanations}
  \end{enumerate}
\item pg 13 ln 35. “However too little results are
  statistically significant.” Does this imply that they model is not
  useful/good? A little more explanation would be helpful.
  \debug{SR: For more explanations I reestimated Model2 for unemployment for the age groups.
I made new folder in dropbox:Tabels4_5. Here are Estimates for the age groups for 4 sub-periods, for time period 2000-2012 and for time period 1989-2012. I also made some changes in the text.}
\item pg 15 ln 60(?) “, but not precisely estimated.” More explanation on what you mean here would be helpful.
\end{enumerate}

### 2018-07-04 paper/ijm.tex
Changed the tables to have the same number of observations. Corrected the text for adding occupation to Model 3.

The central results for unemployment regressions are given in
\cref{tab:unemployment_estimation_by_sex_and_ethnic}.

@@

\begin{table}[t!]
	\begin{center}
		\caption{Estimation results for unemployment.}
		\label{tab:unemployment_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
		\begin{tabular}{l D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad\qquad}
				D{.}{.}{3} @{\qquad} D{.}{.}{3}}
			\toprule
			&         \multicolumn{2}{c}{Men}         &        \multicolumn{2}{c}{Women}        \\
			Estonians:      & \multicolumn{1}{c}{1}      & \multicolumn{1}{l}{\hspace{10pt}2} & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      \\
			Russian         & -0.026^{***}               & -0.010                             & -0.009^{*}                 & 0.010^{**}                 \\
			                & (0.006)                    & (0.006)                            & (0.005)                    & (0.005)                    \\
			English         & -0.047^{***}               & -0.019^{***}                       & -0.024^{***}               & -0.008^{*}                 \\
			                & (0.004)                    & (0.005)                            & (0.004)                    & (0.004)                    \\
			\# observations          & \multicolumn{1}{c}{36,160} & \multicolumn{1}{l}{36,132}         & \multicolumn{1}{l}{36,050} & \multicolumn{1}{c}{36,015} \\
			$R^{2}$         & 0.022                      & 0.047                              & 0.012                      & 0.036                      \\ \hline
			Russians: & \\
			Estonian        & -0.052^{***}               & -0.052^{***}                       & -0.065^{***}               & -0.045^{***}               \\
			                & (0.010)                    & (0.011)                            & (0.009)                    & (0.010)                    \\
			English         & -0.020                     & 0.006                              & -0.015                     & -0.003                     \\
			                & (0.012)                    & (0.014)                            & (0.011)                    & (0.012)                    \\
			\# observations          & \multicolumn{1}{c}{12,946} & \multicolumn{1}{l}{12,942}         & \multicolumn{1}{l}{13,689} & \multicolumn{1}{c}{13,674} \\
			$R^{2}$         & 0.033                      & 0.066                              & 0.023                      & 0.043                      \\ \hline
			year dummies    & \V                         & \V                                 & \V                         & \V                         \\
			indiv. charact. &                            & \V                                 &                            & \V                         \\
			\bottomrule
		\end{tabular}%
		\begin{flushleft}
			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses.\\  Individual characteristics are \modelTwo. \\ \restrictions}
		\end{flushleft}
	\end{center}

@@

\subsection{Wage Regressions}
\label{subsec:basic_model_wage}

\cref{tab:wage_estimation_by_sex_and_ethnic} presents the main
results.

The table
confirms that wage is positively associated with fluency in other
languages, in particular English. The only remarkable exception is
Estonian language for Russian men where we fail to find any positive
effect for any model. This qualitatively repeats the results of
\citet{Toomet2011}. However, for women we observe a sizeable
positive effect between 12 and 16 percentage points, suggesting that
\citet{Toomet2011} results only describe the male labour market.  The effect decreases somewhat
(from 0.167 to 0.114) when including the individual characteristics
into the model, suggesting that the premium
is partly caused by education and potentially also by unobserved
individual performance. Observable workplace characteristics do not
influence the estimates.

@@

@@

			Russian            & 0.107^{***}                & 0.072^{***}                & 0.054^{***}                        & 0.096^{***}                & 0.041^{***}                & 0.035^{***}                \\
			                   & (0.015)                    & (0.015)                    & (0.014)                            & (0.011)                    & (0.011)                    & (0.010)                    \\
			English            & 0.343^{***}                & 0.162^{***}                & 0.145^{***}                        & 0.311^{***}                & 0.131^{***}                & 0.123^{***}                \\
			                   & (0.013)                    & (0.015)                    & (0.013)                            & (0.010)                    & (0.010)                    & (0.010)                    \\
			\# observations             & \multicolumn{1}{l}{22,290} & \multicolumn{1}{l}{22,274} & \multicolumn{1}{l}{21,785}         & \multicolumn{1}{l}{26,673} & \multicolumn{1}{l}{26,644} & \multicolumn{1}{c}{26,449} \\
			$R^{2}$            & 0.726                      & 0.755                      & 0.790                              & 0.769                      & 0.810                      & 0.830                      \\ \midrule

@@

			Estonian           & 0.018                      & -0.014                     & 0.008                              & 0.167^{***}                & 0.114^{***}                & 0.125^{***}                \\
			                   & (0.018)                    & (0.019)                    & (0.018)                            & (0.014)                    & (0.014)                    & (0.014)                    \\
			English            & 0.249^{***}                & 0.155^{***}                & 0.137^{***}                        & 0.223^{***}                & 0.089^{***}                & 0.089^{***}                \\
			                   & (0.026)                    & (0.027)                    & (0.026)                            & (0.021)                    & (0.022)                    & (0.020)                    \\
			\# observations             & \multicolumn{1}{l}{8234}   & \multicolumn{1}{l}{8233}   & \multicolumn{1}{l}{7978}           & \multicolumn{1}{l}{9904}   & \multicolumn{1}{l}{9895}   & \multicolumn{1}{c}{9697}   \\
			$R^{2}$            & 0.731                      & 0.746                      & 0.783                              & 0.794                      & 0.809                      & 0.837                      \\ \hline

>>>>

The central results for unemployment regressions are given in
\cref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}.
\footnote{This table is restricted to have the same number of observations across all models requested by reviewer. The unrestricted table is in the appendix \cref{tab:unemployment_estimation_by_sex_and_ethnic}.}

@@

\begin{table}[t!]
	\begin{center}
		\caption{Estimation results for unemployment.}
		\label{tab:unemployment_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
		\begin{tabular}{l D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad\qquad}
				D{.}{.}{3} @{\qquad} D{.}{.}{3}}
			\toprule
			&         \multicolumn{2}{c}{Men}         &        \multicolumn{2}{c}{Women}        \\
			Estonians:      & \multicolumn{1}{c}{1}      & \multicolumn{1}{l}{\hspace{10pt}2} & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      \\
			Russian         & -0.026^{***}               & -0.001                             & -0.009^{*}                 & 0.010^{**}                 \\
			                & (0.006)                    & (0.006)                            & (0.005)                    & (0.005)                    \\
			English         & -0.047^{***}               & -0.019^{***}                       & -0.024^{***}               & -0.008^{*}                 \\
			                & (0.004)                    & (0.005)                            & (0.004)                    & (0.004)                    \\
			\# observations          & \multicolumn{1}{c}{36,132} & \multicolumn{1}{l}{36,132}         & \multicolumn{1}{l}{36,015} & \multicolumn{1}{c}{36,015} \\
			$R^{2}$         & 0.022                      & 0.047                              & 0.012                      & 0.036                      \\ \hline
			Russians: & \\
			Estonian        & -0.052^{***}               & -0.052^{***}                       & -0.065^{***}               & -0.045^{***}               \\
			                & (0.010)                    & (0.011)                            & (0.009)                    & (0.010)                    \\
			English         & -0.020                     & 0.006                              & -0.014                     & -0.003                     \\
			                & (0.012)                    & (0.014)                            & (0.011)                    & (0.012)                    \\
			\# observations          & \multicolumn{1}{c}{12,942} & \multicolumn{1}{l}{12,942}         & \multicolumn{1}{l}{13,674} & \multicolumn{1}{c}{13,674} \\
			$R^{2}$         & 0.033                      & 0.066                              & 0.023                      & 0.043                      \\ \hline
			year dummies    & \V                         & \V                                 & \V                         & \V                         \\
			indiv. charact. &                            & \V                                 &                            & \V                         \\
			\bottomrule
		\end{tabular}%
		\begin{flushleft}
			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses.\\  Individual characteristics are \modelTwo. \\ \restrictions}
		\end{flushleft}
	\end{center}

@@

\subsection{Wage Regressions}
%SKB: Adding occupation to Model 3 reduces the effects drastically. Beforehand I somehow forgot to add it to the estimation. Now occupation is included as it should have been in the first place.
\label{subsec:basic_model_wage}

\cref{tab:wage_estimation_by_sex_and_ethnic_same_sample} presents the main
results.\footnote{This table is restricted to have the same number of observations across all models requested by reviewer. The unrestricted table is in the appendix \cref{tab:wage_estimation_by_sex_and_ethnic}.}

The table
confirms that wage is positively associated with fluency in other
languages, in particular English. The only remarkable exception is
Estonian language for Russian men where we fail to find any positive
effect for any model. This qualitatively repeats the results of
\citet{Toomet2011}. However, for women we observe a sizeable
positive effect between 6 and 16 percentage points, suggesting that
\citet{Toomet2011} results only describe the male labour market.  The effect decreases somewhat
(from 0.167 to 0.114) when including the individual characteristics
into the model, suggesting that the premium
is partly caused by education and potentially also by unobserved
individual performance. Adding further observable workplace characteristics nearly halves the effects 
(when accounting not only for the industry but also the occupation) %SKB: Might remove this sentence
.

@@

		%Accounting for occupation in model reduced the Estonian coefficient for women drastically (from 0.12 down 0.06)!
		%For other groups it is less

@@

			Russian            & 0.112^{***}                & 0.078^{***}                & 0.043^{***}                        & 0.094^{***}                & 0.039^{***}                & 0.016^{*}                \\
			                   & (0.015)                    & (0.015)                    & (0.014)                            & (0.011)                    & (0.011)                    & (0.009)                    \\
			English            & 0.343^{***}                & 0.158^{***}                & 0.108^{***}                        & 0.311^{***}                & 0.130^{***}                & 0.075^{***}                \\
			                   & (0.013)                    & (0.015)                    & (0.013)                            & (0.010)                    & (0.010)                    & (0.009)                    \\
			\# observations             & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{21,785} & \multicolumn{1}{l}{21,785}         & \multicolumn{1}{l}{26,673} & \multicolumn{1}{l}{26,644} & \multicolumn{1}{c}{26,449} \\
			$R^{2}$            & 0.730                      & 0.760                      & 0.801                              & 0.769                      & 0.810                      & 0.830                      \\ \midrule

@@

			Estonian           & 0.020                      & -0.013                     & -0.009                              & 0.167^{***}                & 0.114^{***}                & 0.066^{***}                \\
			                   & (0.018)                    & (0.019)                    & (0.018)                            & (0.014)                    & (0.014)                    & (0.013)                    \\
			English            & 0.248^{***}                & 0.152^{***}                & 0.103^{***}                        & 0.223^{***}                & 0.089^{***}                & 0.054^{***}                \\
			                   & (0.026)                    & (0.027)                    & (0.024)                            & (0.021)                    & (0.022)                    & (0.018)                    \\
			\# observations             & \multicolumn{1}{l}{7978}   & \multicolumn{1}{l}{7978}   & \multicolumn{1}{l}{7978}           & \multicolumn{1}{l}{9904}   & \multicolumn{1}{l}{9895}   & \multicolumn{1}{c}{9697}   \\
			$R^{2}$            & 0.731                      & 0.746                      & 0.794                              & 0.794                      & 0.809                      & 0.854                      \\ \hline
